Reconstructing Propositional Proofs in Type Theory

### 2017-10-27 paper/sections/proof-reconstruction.tex
Cosmetic changes.
[ paper ] more corrections.

\begin{notation}
The function name written in \texttt{typewriter} font refers to
a \Metis inference rule.
The same function name written using \textsf{sans serif} refers to the proposed
version of the rule implemented in \cite{AgdaProp,AgdaMetis}.
\end{notation}

@@

The pattern of the formalization for this rule is the following.
For \conjunct rule, we define in type theory a function using the same name,
conjunct, but written using roman font to distinguish from the original.
The \fconjunct function has the following pattern:

 \begin{equation*}
  \begin{aligned}
  &\hspace{.495mm}\fconjunct : \Prop → \Prop → \Prop\\
  &\begin{array}{ll}
  \fconjunct~φ~ψ\ &=
      \begin{cases}
      ψ, &\text{if }\fconjunct \text{ built }ψ\text{ by applying valid}\\
         &\text{transformations or other rules to }φ\\
      φ, &\text{otherwise.}
      \end{cases}
  \end{array}
  \end{aligned}
  \end{equation*}

\begin{itemize}
  \item[∙] $φ$ is the \emph{source} formula from a previous deducted derivation.
  \item[∙] $ψ$ is the \emph{target} formula. The expected result of \texttt{rule}.
\end{itemize}

To justify all transformations done by \fconjunct, we prove its soundness
with a theorem. This theorem would be

\begin{equation*}
\text{If }Γ ⊢ φ\text{ then }Γ ⊢ \fconjunct~φ~ψ.
\end{equation*}

@@

The remainder of this section will be devoted to present a formal description
in type theory of each rule presented in Table~\ref{tab:agda-metis-table} using
the pattern present in the example above.

>>>>

\begin{notation}

The function name written in \texttt{typewriter} font refers to a \Metis
inference rule. The same function name written using \textsf{sans serif} font
refers to our proposed version to reconstruct the rule and implemented
in~\cite{AgdaMetis}. We use \Source and \Target as synonyms of \Prop type to
describe in the function type the role of the arguments.

\end{notation}

@@

The pattern of the formalization for this rule is the following. For the
\conjunct rule, we define in type theory a function using the same name,
\fconjunct, but written using \textsf{san serif} font to distinguish from the
original. The \fconjunct function has the following pattern:

 \begin{equation*}
  \begin{aligned}
  &\hspace{.495mm}\fconjunct : \Source → \Target → \Prop\\
  &\begin{array}{ll}
  \fconjunct~φ~ψ\ &=
      \begin{cases}
      ψ, &\text{if }\fconjunct \text{ built }ψ\text{ by applying valid}\\
         &\text{transformations or other rules to }φ;\\
      φ, &\text{otherwise.}
      \end{cases}
  \end{array}
  \end{aligned}
  \end{equation*}

\begin{itemize}
  \item[∙] $φ : \Source$ is the \emph{source} formula from a previous deducted derivation.
  \item[∙] $ψ : \Target$ is the \emph{target} formula. The expected result of the \fconjunct rule.
\end{itemize}

To justify all transformations done by the \fconjunct rule, we prove its
soundness with a theorem. This theorem would be

\begin{equation*}
\text{If }Γ ⊢ φ\text{ and }ψ : \Target \text{ then }Γ ⊢ \fconjunct~φ~ψ.
\end{equation*}

@@

The remainder of this section will be devoted to present a formal description
in type theory of each rule presented in Table~\ref{tab:agda-metis-table} using the pattern present in the example above.
We follow the same order to present the rules as the table shows.
